Empirical Bayes analysis of \RNAseq{} data for detection of gene expression heterosis

### 2015-08-24 ebayes_rnaseq_heterosis.tex
typo

In addition to the approach of \citeauthor{ji2014estimation}, we modified two existing \RNAseq{} approaches, \edgeR{} and \baqSeq{}, for use in the overdominance context. For each method, we attempted to provide a measure of the strength of overdominance for each gene such that large values of this measure indicate support for heterosis.

@@

\baqSeq{} allows for a wider range of hypotheses for each gene, including $H^*_{g1}: \mu_{g1}=\mu_{g2}=\mu_{g3}$, $H^*_{g 2}: \mu_{g1}=\mu_{g2}$, $H^*_{g 3}: \mu_{g1}=\mu_{g3}$, $H^*_{g 4}: \mu_{g2}=\mu_{g3}$, and $H^*_{g 5}:$ all $\mu_g$'s are distinct. In a technique similar to our application of \edgeR{}, we used the posterior probabilities of these hypotheses to construct a measure of heterosis for each gene. We set this measure to zero if the maximum likelihood estimate, calculated using \edgeR{}, of $\mu_{g3}$ is between the maximum likelihood estimates of $\mu_{g1}$ and $\mu_{g2}$. Otherwise, the measure is the sum of the posterior probabilities of $H^*_{g 2}$ and $H^*_{g 5}$, the two hypotheses that allow for overdominance.

>>>>

In addition to the approach of \citeauthor{ji2014estimation}, we modified two existing \RNAseq{} approaches, \edgeR{} and \baySeq{}, for use in the overdominance context. For each method, we attempted to provide a measure of the strength of overdominance for each gene such that large values of this measure indicate support for heterosis.

@@

\baySeq{} allows for a wider range of hypotheses for each gene, including $H^*_{g1}: \mu_{g1}=\mu_{g2}=\mu_{g3}$, $H^*_{g 2}: \mu_{g1}=\mu_{g2}$, $H^*_{g 3}: \mu_{g1}=\mu_{g3}$, $H^*_{g 4}: \mu_{g2}=\mu_{g3}$, and $H^*_{g 5}:$ all $\mu_g$'s are distinct. In a technique similar to our application of \edgeR{}, we used the posterior probabilities of these hypotheses to construct a measure of heterosis for each gene. We set this measure to zero if the maximum likelihood estimate, calculated using \edgeR{}, of $\mu_{g3}$ is between the maximum likelihood estimates of $\mu_{g1}$ and $\mu_{g2}$. Otherwise, the measure is the sum of the posterior probabilities of $H^*_{g 2}$ and $H^*_{g 5}$, the two hypotheses that allow for overdominance.
